% !TEX program = xelatex

\documentclass{resume}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Damien Plenard}

\basicInfo{
  \email{damien@plenard.me} \textperiodcentered\
  \github[github.com/damoun]{https://github.com/damoun} \textperiodcentered\
  \linkedin[linkedin.com/in/dplenard]{https://www.linkedin.com/in/dplenard}
}

\section{\texorpdfstring{\textbf{\faicon{user-circle}}\ Professional Summary}{Professional Summary}}

Senior Site Reliability Engineer with 14+ years of experience architecting and
operating mission-critical infrastructure at scale. Proven expertise in cloud
platforms (AWS, GCP), Infrastructure as Code, container orchestration, and
observability solutions. Strong track record of improving system reliability,
automating operations, and championing SRE culture across engineering organizations.

\section{\texorpdfstring{\textbf{\faicon{cogs}}\ Skills}{Skills}}

\begin{itemize}[parsep=0.5ex]
  \item \textbf{Cloud \& Infrastructure:} AWS, GCP, On-Premises
  \item \textbf{Containers \& Orchestration:} Kubernetes, Nomad, Docker
  \item \textbf{IaC \& Configuration:} Terraform, Ansible, Helm, FluxCD
  \item \textbf{CI/CD:} GitLab CI, GitHub Actions, Git
  \item \textbf{Observability:} Prometheus, Grafana, DataDog, Elasticsearch
  \item \textbf{Languages:} Golang, Python, Bash
  \item \textbf{Databases \& Messaging:} Elasticsearch, RabbitMQ, Redis
\end{itemize}

\section{\texorpdfstring{\textbf{\faicon{user}}\ Experience}{Experience}}

\datedsubsection{\textbf{Camunda}}{Apr. 2024 -- Present}
\role{Senior Site Reliability Engineer}{Amsterdam}
Ensure availability and reliability of multi-tenant SaaS platform.

\datedsubsection{\textbf{Mollie}}{Feb. 2022 -- Mar. 2024}
\role{Site Reliability Engineer II}{Amsterdam}
Led infrastructure initiatives during Google Cloud Platform migration for payment processing platform.
\begin{itemize}
  \item Architected and executed disaster recovery strategy for production infrastructure
  \item Automated server provisioning and configuration management using Ansible
  \item Maintained high availability of Kubernetes clusters and on-premises infrastructure
  \item Deployed applications to cloud infrastructure using Terraform and Helm charts
  \item Standardized observability infrastructure through Terraform-managed dashboards
  \item Established SLO framework to improve service reliability posture
  \item Designed resilient architectures for managed RabbitMQ and Elasticsearch clusters
  \item Ensured compliance with fintech security standards and regulatory requirements
  \item Participated in 24/7 on-call rotation supporting production systems
\end{itemize}

\datedsubsection{\textbf{Veepee}}{Jan. 2018 -- Jan. 2022}
\role{Site Reliability Engineer}{Amsterdam}
Delivered observability platform and infrastructure automation for e-commerce operations.
\begin{itemize}
  \item Championed observability culture, driving adoption of SRE practices across engineering teams
  \item Operated 90+ TB Elasticsearch cluster serving APM and centralized logging infrastructure
  \item Built long-term metrics storage solution using Prometheus and Thanos federation
  \item Provisioned and maintained Docker orchestration platform using Nomad, Consul, and Vault
  \item Developed synthetic monitoring solution with Python-based browser testing framework
  \item Streamlined incident response through workflow automation and tooling improvements
\end{itemize}

\datedsubsection{\textbf{Payplug}}{Mar. 2012 -- Dec. 2017}
\role{System Engineer}{Paris \& Amsterdam}
Built and operated carrier billing platform integrations for mobile payment services.
\begin{itemize}
  \item Designed API service for phone number carrier lookup aggregating multiple data sources
  \item Developed microservice application for bulk SMS and premium messaging delivery
  \item Implemented subscription-based billing system for mobile payment processing
  \item Enhanced software quality through improved QA processes and CI/CD pipeline automation
  \item Administered MongoDB and MySQL databases supporting production workloads
\end{itemize}

\datedsubsection{\textbf{Epitech}}{Sept. 2010 -- Mar. 2012}
\role{Teaching Assistant (part-time)}{Paris}
Supported computer science students through coursework and project evaluation.
\begin{itemize}
  \item Evaluated student projects and examinations across multiple programming disciplines
  \item Delivered lectures on C programming, Shell scripting, and system fundamentals
\end{itemize}

\section{\texorpdfstring{\textbf{\faicon{graduation-cap}}\ Education}{Education}}

\datedsubsection{\textbf{Epitech}, Paris}{2014}
\textit{Master of Science} in Computer Science and Engineering

\datedsubsection{\textbf{BJTU}, Beijing}{2013}
\textit{2 Semesters} in Computer Science and Engineering

\section{\texorpdfstring{\textbf{\faicon{info}}\ Additional}{Additional}}
\begin{itemize}[parsep=0.5ex]
  \item Maintain personal HomeLab for hands-on experimentation with emerging technologies
  \item Built and grew Twitch streaming community to 2K+ followers
  \item Serve as elected board member for residential community association (VvE)
\end{itemize}

\end{document}
